Figures and tables for paper

### 2021-12-02 analysis/04_figs-tables.Rmd

intib <- read_rds(
    here::here("analysis", "output", "posterior_draws", "interactions.rds")
  )
```

@@

contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = oxfam_criticized - amnesty_criticized,
    oxfam_greenpeace_criticized = oxfam_criticized - greenpeace_criticized,
    red_cross_amnesty_criticized = red_cross_criticized - amnesty_criticized,
    red_cross_greenpeace_criticized = red_cross_criticized - greenpeace_criticized,
    oxfam_amnesty_crackdown = oxfam_crackdown - amnesty_crackdown,
    oxfam_greenpeace_crackdown = oxfam_crackdown - greenpeace_crackdown,
    red_cross_amnesty_crackdown = red_cross_crackdown - amnesty_crackdown,
    red_cross_greenpeace_crackdown = red_cross_crackdown - greenpeace_crackdown
  )
# Plot the contrasts
contrasts_int %>%
  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

>>>>

intib <- read_rds(
    here::here("analysis", "output", "posterior_draws", "interactions.rds")
  )

# Storing intercept draws in a different tibble for easier use; emergency response, no financial transparency, no accountability, many private donors and friendly relationship with government are all reference levels for their respective groups, and thus are not found in the tibble.
dtib <- tibble(
  amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(i == 2) %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(i == 3) %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(i == 9) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull()
)
```

@@

contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
    oxfam_greenpeace_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
    red_cross_amnesty_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
    red_cross_greenpeace_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
    oxfam_amnesty_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
    oxfam_greenpeace_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown),
    red_cross_amnesty_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
    red_cross_greenpeace_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown)
  )
# Plot the contrasts
contrasts_int %>%
  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

```{r crackdown-contrasts-b-alt}
# Pull the posterior draws for organization*government crackdown interaction

contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized),
    oxfam_greenpeace_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized),
    red_cross_amnesty_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized),
    red_cross_greenpeace_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized),
    oxfam_amnesty_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown),
    oxfam_greenpeace_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown),
    red_cross_amnesty_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown),
    red_cross_greenpeace_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown)
  )
# Plot the contrasts
contrasts_int %>%
  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis02b_alt.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
 )
```
